Proportional multi-state multiple-cohort life table model

### 2018-04-13 MSLT/MSLTdoc.Rmd
Graphs GBD data for greater London and England

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
    - \usepackage{float}
    - \usepackage{pdflscape}
    - \newcommand{\blandscape}{\begin{landscape}}
    - \newcommand{\elandscape}{\end{landscape}}
output:
   pdf_document: 
     toc: true
     toc_depth: 3
     number_sections: true

     df_print: kable
   fontsize: 12 pt
   geometry: margin=1in
bibliography: Bibliography.bib
---

>>>>

---
title: "Proportional multi-state multiple-cohort life table model"
author: "Belen Zapata-Diomedi and Ali Abbas"
date: "26 March 2018"
header-includes:
    - \usepackage{setspace}\onehalfspacing
    - \usepackage{float}
    - \usepackage{pdflscape}
    - \newcommand{\blandscape}{\begin{landscape}}
    - \newcommand{\elandscape}{\end{landscape}}
output:
   pdf_document: 
     toc: true
     toc_depth: 3
     number_sections: true
     df_print: kable
   fontsize: 12 pt
   geometry: margin=1in
bibliography: Bibliography.bib
---
